\textbf{ Matching the forecast horizon with the relevant ecological processes }

### 2019-09-13 doc/manuscript.tex
Acknowledgements

We made forecasts based on two phenomenological models, each representing processes operating at different time scales. 
The first phenomenological model represents the space-for-time substiution approach, which we call the ``spatial approach'' for brevity. 
We correlated the mean environment with the mean of an ecological state or rate across many sites. The second model represents the time-series or ``temporal approach.'' We correlated interannual variation in an ecological response with interannual variation in the environment at just one site. 
We compared forecasts from both models to the simulated dynamics to determine how well the two approaches perform at different forecast horizons. We also assessed the potential for combining the information available in both spatial and temporal patterns by using a weighted average of the forecasts from the spatial and temporal approaches optimized to best match the (simulated) observations. We then studied how the optimal model weights changed over time. These spatial, temporal and combined statistical
models are described in Appendix \ref{models}. We expected the temporal model to best predict short-term dynamics, the spatial model to best predict long-term dynamics, and that a combination of the two approaches would provide the best forecasts at transitional, intermediate time scales.

@@

>>>>

We made forecasts based on two phenomenological models, each representing processes operating at different time scales. 
The first phenomenological model represents the space-for-time substiution approach, which we call the ``spatial approach'' for brevity. 
We correlated the mean environment with the mean of an ecological state or rate across many sites. The second model represents the time-series or ``temporal approach.'' We correlated interannual variation in an ecological response with interannual variation in the environment at just one site. We compared forecasts from both models to the simulated dynamics to determine how well the two approaches perform at different forecast horizons. We also assessed the potential for combining the information available in both spatial and temporal patterns by using a weighted average of the forecasts from the spatial and temporal approaches optimized to best match the (simulated) observations. We then studied how the optimal model weights changed over time. We expected the temporal model to best predict short-term dynamics, the spatial model to best predict long-term dynamics, and that a combination of the two approaches would provide the best forecasts at transitional, intermediate time scales. The spatial, temporal and combined statistical models are described in Appendix \ref{models} and all code for both case studies is available at Github (https://github.com/pbadler/space-time-forecast).

@@

\subsubsection*{Acknowledgements}

We thank Heather Lynch and Juan Manuel Morales for comments that improved early drafts of the paper. PBA was supported by NSF DEB-1927282 and the Utah Agriculture Experiment Station, EPW was supported by ??, and MHC was supported by ??.
